Enriching Object Detection with 2D-3D Registration\\and Continuous Viewpoint Estimation

### 2014-11-14 intro.tex
typo and capion4

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truly continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.

>>>>

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing and we call these NZ-WHO templates \ref{fig:front}. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truly continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.
